Introduction to LLL\\``Cryptography''

### 2021-06-03 paper.tex
Add gram-schmidt and gauss reduction algorithm2e

\usepackage{alltt, fancyvrb, url}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{subfigure}
\usepackage{wrapfig}
\usepackage{algorithm}% http://ctan.org/pkg/algorithms
%\usepackage{algorithmicx}
\usepackage[utf8]{inputenc}
\usepackage{fontenc}
\usepackage{amsmath,stmaryrd,mathtools,algorithm}
\usepackage{amssymb}
%\usepackage{amsfonts}
\usepackage{float}
\usepackage{hyperref}
\usepackage{listings}
\usepackage{url}

@@

\begin{algorithm}
    \textbf{Gram-Schmidt Algorithm}
\end{algorithm}

@@

@@

\begin{algorithm}
    \caption{Gauss Basis Reduction}
    \vspace*{5px}
    \text{Loop} \\
    If $\lVert v_2 \rVert < \lVert v_1 \rVert$ , \text{swap }$v_1, v_2$ \\
    m = $\left \lceil{(v_1 \cdot v_2) {\lVert v_1 \rVert}^{-2}} \right \rceil$ \\
    \text{If } $m = 0$, \text{return } $v_1, v_2$ \\
    $v_2 = v_2 - mv_1$ \\
    \text{Continue Loop}
\end{algorithm}

\begin{figure}[b]
    \centering
    \includegraphics[width=0.5\textwidth]{./img/gauss_svp.png}
    \caption{Gauss reduction}
    \label{fig:gauss_svp}
\end{figure}

@@

@@

However the bigger the dimension of the lattice, the harder is the problem and there isn't a polynomial algorithm to find such vector.

>>>>

\usepackage{alltt, fancyvrb, url}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{subfigure}
\usepackage{wrapfig}
% \usepackage{algorithm}% http://ctan.org/pkg/algorithms
% \usepackage[ruled,vlined]{algorithm2e}
% \usepackage{algorithm}
\usepackage[]{algorithm2e}
\usepackage{algorithmic}
\usepackage[utf8]{inputenc}
\usepackage{fontenc}
\usepackage{amsmath,stmaryrd,mathtools,algorithm}
\usepackage{amssymb}
%\usepackage{amsfonts}
\usepackage{float}
\usepackage{hyperref}
\usepackage{listings}
\usepackage{url}

@@

\begin{algorithm}[H]
    \vspace*{5px}
    $v_1^* = v1$\;
    \\
    \For{$i \gets 2$ \KwTo $n$}{
        $\mu_{ij} = v_i \cdot v_j^* / \lVert v_j^* \rVert ^ 2$ for $1 \le j < i$ \;
        \\
        $v_i^* = v_i - \sum_{j=1}^{i-1} \mu_{ij}v_j^*$ \;
    }
    \caption{Gram-Schmidt Algorithm}
\end{algorithm}

@@

\clearpage

@@

\begin{figure}[!b]
    \centering
    \includegraphics[width=0.5\textwidth]{./img/gauss_svp.png}
    \caption{Gauss reduction}
    \label{fig:gauss_svp}
\end{figure}

@@

\begin{algorithm}[H]
    \vspace*{5px}
    \While{true}{
        \If{$\lVert v_2 \rVert < \lVert v_1 \rVert$}{
            swap $v_1, v_2$ \;
        }
        m = $\left \lfloor{(v_1 \cdot v_2) {\lVert v_1 \rVert}^{-2}} \right \rfloor$ \\
        \If{$m = 0$}{
            return $v_1, v_2$ \;
        }
        $v_2 = v_2 - mv_1$ \\
    }
    \caption{Gauss Basis Reduction}
\end{algorithm}

@@

The bigger the dimension of the lattice, the harder is the problem and there isn't a polynomial algorithm to find such vector.
